Case Study: Gene Set Enrichment Analysis (Mouse Data Set)

### 2018-03-22 datasets/GSEA/gsea-human.Rmd
Download GSEA input data from pk dropbox

Download *DESeqDataSet* if not present locally.

```{r, message=FALSE}
if (!file.exists(count_file)) {
    ## download.file("", destfile = count_file)
}
dsdObject <- readRDS(count_file)
```

**What are we doing here?**

```{r}
levels(colData(dsdObject)$individual) <- gsub("GTEX-", "", levels(colData(dsdObject)$individual))
```

>>>>

**Some sort of summary of the data set.**  
We download a *DESeqDataSet* if not present locally.

```{r, message=FALSE}
if (!file.exists(count_file)) {
    download.file("https://www.dropbox.com/s/itrs2a6cnmurnck/human-counts.rds?dl=1",
                  destfile = count_file)
}
dsdObject <- readRDS(count_file)
```

### 2018-03-22 datasets/GSEA/gsea-mouse.Rmd
Download GSEA input data from pk dropbox

```{r, message=FALSE}
if (!file.exists(count_file)) {
    ## download.file("", destfile = count_file)
}
dseHSCMPP <- readRDS(count_file)
```

>>>>

```{r, message=FALSE}
if (!file.exists(count_file)) {
    download.file("https://www.dropbox.com/s/jq6giqeclxcdypq/mouse-counts.rds?dl=1",
                  destfile = count_file)
}
dseHSCMPP <- readRDS(count_file)
```
